Predicting How Well Exercise is Performed
=========================================

Author: Harry J. Braviner


This document is my project writeup for the Coursera Data Science course Practical Machine Learning.


The dataset used for this model is described [here](http://groupware.les.inf.puc-rio.br/har).

## Building the model

We begin by reading in our training dataset.
```{r, echo = TRUE}
training <- read.csv('pml-training.csv')
nrow(training) 
```
A glance at the data reveals several variable in which almost all entries as `NA` (e.g. `max_roll_dumbell`) and several that have missing values masked by their conversion to factor variables (e.g. `kurtosis_roll_belt`).
```{r, echo = TRUE}
cleanCols <- !(apply(training, 2, function(x) {any(is.na(x) || x == "" || x == "#DIV/0!")}))
numCleanCols <- sum(cleanCols)
```
Removing these columns with poor quality data, we are left with `r numCleanCols` variables, and we build a reduced training set which we call `train` for brevity.
I also remove the `user_name` field, since I don't want to train to individual users,
the timestamp fields, since I suspect these don't matter (a real user may be more tired at certain times, but these subjects are being told to make deliberate mistakes),
and the `X`, `new_window` and `num_window` fields, since I don't really know what these are, which is reason enough to remove them.
```{r, echo = TRUE}
train <- training[,cleanCols]
names(train, 10)
train <- training[,8:ncol(train)]
```
